---
title: "r-draft-1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
rm(list = ls(all.names = TRUE))
```

```{r}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
```

# Import dataset 1

Additional Note:
Field ids are unique within a .csv file but are not necessarily unique across all files.

```{r}
# device info
d1_device <- read.csv("dataset1/device_info.csv")

# http info
d1_http <- read.csv("dataset1/http_info.csv")

# logon info
d1_logon <- read.csv("dataset1/logon_info.csv")
```


### device_info.csv (~66k records)
* Fields: id, date, user, pc, activity (connect/disconnect)
* Some users use a portable zip drive
* Some connect(s) may be missing disconnect(s), since machine may be turned off without a proper disconnect. 

```{r}
#d1_device


```


### HTTP_info.csv (~3.5M records)
* Fields: id, date, user, pc, url
* Up to 15 URLs visited daily between daily logon and daily logoff
* Up to 5 URLs visited daily after-hours

```{r}
#d1_http


```


### logon_info.csv (~850k records)
* Fields: id, date, user, pc, activity (Logon/Logoff)
* Logoff requires preceding logon
* Each user has an assigned machine, but can share others
* 100 machines shared (physically shared) by some of the users in addition to their assigned PC. 
* Some logons occur after-hours 
*Note: Screen unlocks are recorded as logons. Screen locks are not recorded.
* 12 of the users are IT administrators

```{r}
#d1_logon


```



### Employees_info Folder
* 18 Employee files (~1k records each file)
  - Fields: employee_name, user_id, email, domain, role
  - Record of who is employed at the end of the month 

```{r}
# employee info (year, month)
e1.09.12 <- read.csv("dataset1/Employees_info/2009-12.csv")
e1.10.01 <- read.csv("dataset1/Employees_info/2010-Jan.csv")
e1.10.02 <- read.csv("dataset1/Employees_info/2010-Feb.csv")
e1.10.03 <- read.csv("dataset1/Employees_info/2010-Mar.csv")
e1.10.04 <- read.csv("dataset1/Employees_info/2010-Apr.csv")
e1.10.05 <- read.csv("dataset1/Employees_info/2010-May.csv")
e1.10.06 <- read.csv("dataset1/Employees_info/2010-Jun.csv")
e1.10.07 <- read.csv("dataset1/Employees_info/2010-Jul.csv")
e1.10.08 <- read.csv("dataset1/Employees_info/2010-Aug.csv")
e1.10.09 <- read.csv("dataset1/Employees_info/2010-Sep.csv")
e1.10.10 <- read.csv("dataset1/Employees_info/2010-Oct.csv")
e1.10.11 <- read.csv("dataset1/Employees_info/2010-Nov.csv")
e1.10.12 <- read.csv("dataset1/Employees_info/2010-Dec.csv")
e1.11.01 <- read.csv("dataset1/Employees_info/2011-Jan.csv")
e1.11.02 <- read.csv("dataset1/Employees_info/2011-Feb.csv")
e1.11.03 <- read.csv("dataset1/Employees_info/2011-Mar.csv")
e1.11.04 <- read.csv("dataset1/Employees_info/2011-Apr.csv")
e1.11.05 <- read.csv("dataset1/Employees_info/2011-May.csv")
```

```{r}

```

