---
title: "r-draft-logon"
output: 
  html_document: 
    fig_height: 3
    fig_width: 5
    keep_md: yes
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, size = "small")
knitr::opts_knit$set(root.dir = "../")
#rm(list = ls(all.names = TRUE))
```

```{r}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
```

# Import dataset2
  - logon info

```{r}
# logon info (55.8 MB)
logon <- read.csv("dataset2/logon_info.csv")
```

## logon.csv (~ records)
* Fields: id, date, user, pc, activity (Logon/Logoff)
* some logons have been removed from the dataset, to mimic a “messy” scenario
* Each user has an assigned machine, but can share others
* 100 machines shared (physically shared) by some of the users in addition to their assigned PC. 
* Some logons occur after-hours 
*Note: Screen unlocks are recorded as logons. Screen locks are not recorded.

```{r}
# logon info
head(logon)

dim(logon)

str(logon)

# check for missing values
table(is.na(logon))

summary(logon)

```
