---
title: "r-draft-email"
output: 
  html_document: 
    fig_height: 3
    fig_width: 5
    keep_md: yes
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, size = "small", message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "../")
#rm(list = ls(all.names = TRUE))
```

```{r}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
```


```{r}
# email info (1.3 GB)
email <- read.table("dataset2/email_info.csv", header = TRUE, sep = ",", as.is = TRUE)

email$date <- strptime(email$date, "%m/%d/%Y %T")
```

## email_info (~2.6M records)
* VERY IMPORTANT
* Fields: id, date, user, pc, to, cc, bcc, from, size, attachment_count, content
* Per usual, emails can have multiple recipients
* Emails can be sent to non-employees. The company name is randomly initialized DTAA (there isn’t any significance here), and can be used to identify other employees.
* Email size is in bytes, not including any possible attachments.
* Emails have carbon copy info.
* Per usual - content and subjects may not match 

```{r}
# email info
head(email)

dim(email)

str(email)

# check for missing values
table(is.na(email))

summary(email)

```

