---
title: "r-draft-2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
rm(list = ls(all.names = TRUE))
```

```{r}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
```

# Import dataset 2

Comments:
* Employees interests can change over time.
* Scenarios are plentiful in this dataset, so finding 1 interesting “thing” would be the absolute minimum.



file.csv
Fields: id, date, user, pc, filename, content
* Each item represents an item copied to a thumb-drive
* Files are summarized by keywords of the “content”

http.csv
* Fields: id, date, user, pc, url, content
* content has a set of key words which relate to the site.
* Per-usual, webpages can have multiple topics
* Websites have been randomly generated, some may be real sites, others not. Exercise care when visiting websites. 

logon.csv
* Fields: id, date, user, pc, activity (Logon/Logoff)
* some logons have been removed from the dataset, to mimic a “messy” scenario
* Each user has an assigned machine, but can share others
* 100 machines shared (physically shared) by some of the users in addition to their assigned PC. 
* Some logons occur after-hours 
*Note: Screen unlocks are recorded as logons. Screen locks are not recorded.

psychometric.csv
* Fields: employee_name, user_id, O, C, E, A, N
* Big 5 psychometric score
* OCEAN describes the Big-5 personality traits. You’ll want to examine extraneous materials to understand the significance of each personality type.






device.csv
* Fields: id, date, user, pc, activity (connect/disconnect)
* Some users use a portable zip drive
* Some connect(s) may be missing disconnect(s), since machine may be turned off without a proper disconnect. 

```{r}
# device info
#d2_device

```

email.csv
* Fields: id, date, user, pc, to, cc, bcc, from, size, attachment_count, content
* Per usual,emails can have multiple recipients
* Emails can be sent to non-employees. The company name is randomly initialized DTAA (there isn’t any significance here), and can be used to identify other employees.
* Email size is in bytes, not including any possible attachments.
* Emails have carbon copy info.
* Per usual- content and subjects may not match 
```{r}
# email info
#d2_email <- read.csv("dataset2/email_info.csv")
```



# file info
#d2_file <- read.csv("dataset2/file_info.csv")

# http info
#d2_http <- read.csv("dataset2/http_info.csv")

# logon info
#d2_logon <- read.csv("dataset2/logon_info.csv")

# psychometric info
#d2_psychometric <- read.csv("dataset2/psychometric_info.csv")



```{r}
# device info
d2_device <- read.csv("dataset2/device_info.csv")

# email info
d2_email <- read.csv("dataset2/email_info.csv")

# file info
d2_file <- read.csv("dataset2/file_info.csv")

# http info
d2_http <- read.csv("dataset2/http_info.csv")

# logon info
d2_logon <- read.csv("dataset2/logon_info.csv")

# psychometric info
d2_psychometric <- read.csv("dataset2/psychometric_info.csv")

```








```{r}
# device info
d2_device <- read.csv("dataset2/device_info.csv")
```


```{r}
# email info
d2_email <- read.csv("dataset2/email_info.csv")
```

```{r}
# file info
d2_file <- read.csv("dataset2/file_info.csv")

# http info
d2_http <- read.csv("dataset2/http_info.csv")

# logon info
d2_logon <- read.csv("dataset2/logon_info.csv")

# psychometric info
d2_psychometric <- read.csv("dataset2/psychometric_info.csv")

```


```{r}
# device info
d2_device <- read.csv("dataset2/device_info.csv")

# email info
d2_email <- read.csv("dataset2/email_info.csv")

# file info
d2_file <- read.csv("dataset2/file_info.csv")

# http info
d2_http <- read.csv("dataset2/http_info.csv")

# logon info
d2_logon <- read.csv("dataset2/logon_info.csv")

# psychometric info
d2_psychometric <- read.csv("dataset2/psychometric_info.csv")

```





```{r}
# employee info

e2.09.12 <- read.csv("dataset2/LDAP/2009-12.csv")
e2.10.01 <- read.csv("dataset2/LDAP/2010-01.csv")
e2.10.02 <- read.csv("dataset2/LDAP/2010-02.csv")
e2.10.03 <- read.csv("dataset2/LDAP/2010-03.csv")
e2.10.04 <- read.csv("dataset2/LDAP/2010-04.csv")
e2.10.05 <- read.csv("dataset2/LDAP/2010-05.csv")
e2.10.06 <- read.csv("dataset2/LDAP/2010-06.csv")
e2.10.07 <- read.csv("dataset2/LDAP/2010-07.csv")
e2.10.08 <- read.csv("dataset2/LDAP/2010-08.csv")
e2.10.09 <- read.csv("dataset2/LDAP/2010-09.csv")
e2.10.10 <- read.csv("dataset2/LDAP/2010-10.csv")
e2.10.11 <- read.csv("dataset2/LDAP/2010-11.csv")
e2.10.12 <- read.csv("dataset2/LDAP/2010-12.csv")
e2.11.01 <- read.csv("dataset2/LDAP/2011-01.csv")
e2.11.02 <- read.csv("dataset2/LDAP/2011-02.csv")
e2.11.03 <- read.csv("dataset2/LDAP/2011-03.csv")
e2.11.04 <- read.csv("dataset2/LDAP/2011-04.csv")
e2.11.05 <- read.csv("dataset2/LDAP/2011-05.csv")
```

